---
title: "Random Effects LogLink Logistic regression AQI data"
author: "Michael Andreae"
date: "July, 24, 2015"
output: pdf_document
---

# Insurance status predicts antiemetic use 
We investigate the Hypothesis that insurance status predicets antiemetic use the population in the Public Use File of the Anestehsia Quality Institute with electronic anesthesia records recording antiemetic use.



```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(lme4)
# library(nlme)
```



```{r, global_options, echo=FALSE}

# set the directory to the project directory
setwd("C:/Users/Micheal/Dropbox/Professional/AQI/AQI_RegressionAnalysis")

# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
```

## Load cleaned dataset *fullAQI_4_14* and *prov1_AQI_4_14*
 
we load the cleaned larger dataset without and with provider information *fullAQI_4_14.Rdata*, *prov1_AQI_4_14*, which we generated in *import_AQI_14Jul2015.Rmd*   


```{r, load_clean_dataset, echo=TRUE}
rm(list = ls())
load("Analysis/Data/fullAQI_4_14.Rdata")
load("Analysis/Data/prov1_AQI_4_14.Rdata")
str(fullAQI_4_14)
str(prov1_AQI_4_14)

```

# Logistic Model 3 Link : log, random effects 

We try to fit a **mixed effects** logistic regression model with the a **log** link, using with glmer (lme4 package), with the 

formula <- ond ~ pay +age_group +sex +ASA +anes_type +duration +practice  

**plus** additional random effects for practice and provider

# Random effect provider

## Log Link

Estimate with **one** (random) intercept: 

```{r, log0, eval = FALSE, echo=TRUE}

formula0 <- ond ~ pay +(1|provider)

system.time( 
            fit_log0 <- glmer(formula0, 
             family = binomial(link = "log"), 
             data = prov1_AQI_4_14)
             )
# system.time(for(i in 1:100) mad(runif(1000)))
summary(fit_log0)
fit_log0@beta
```

##### Non-Convergence

With and without fixed effects for provider I get the error message
Error message:
*Error: (maxstephalfit) PIRLS step-halvings failed to reduce deviance in pwrssUpdate
*

## LOGIT link

### Random intercept provider: 

```{r, logit0, eval = TRUE, echo=TRUE}

formula_logit0 <- ond ~ pay  +(1|provider)

system.time( fit_logit0 <- glmer(formula_logit0, 
             family = binomial(link = "logit"), 
             data = prov1_AQI_4_14)
             )
# system.time(for(i in 1:100) mad(runif(1000)))
summary(fit_logit0)
```

### Random intercept nested provider| in practice: 

```{r, eval = FALSE, echo=TRUE}

formula_logit <- ond ~ pay  +(provider|practice)

system.time( fit_logit <- glmer(formula_logit, 
             family = binomial(link = "logit"), 
             data = prov1_AQI_4_14)
             )
# system.time(for(i in 1:100) mad(runif(1000)))
summary(fit_logit)
```

Error message

*Error in if (ctrl$npt > (2 * n + 1)) warning("Setting npt > 2 * length(par) + 1 is not recommended.") : 
  missing value where TRUE/FALSE needed*
  
**Really, I do not understand this well enough to do this complicated model.**

Try instead to include more predictors


### Random intercept provider + sex: 

```{r, logit1, eval = TRUE, echo=TRUE}

formula_logit1 <- ond ~ pay + sex  +(1|provider)

system.time( fit_logit1 <- glmer(formula_logit1, 
             family = binomial(link = "logit"), 
             data = prov1_AQI_4_14)
             )
# system.time(for(i in 1:100) mad(runif(1000)))
summary(fit_logit1)
```

### Random intercept provider + sex +age_group: 

```{r, logit2, eval = FALSE, echo=TRUE}

formula_logit2 <- ond ~ pay + sex  +age_group +(1|provider)

system.time( fit_logit2 <- glmer(formula_logit2, 
             family = binomial(link = "logit"), 
             data = prov1_AQI_4_14)
             )
# system.time(for(i in 1:100) mad(runif(1000)))
summary(fit_logit2)
```

##### Non-Convergence

## Random effect practice, fixed effect practice included

```{r, log0_practice, echo=TRUE}

formula0_practice <- ond ~ pay + practice +(1|practice)

system.time( fit_log0_practice <- glmer(formula0_practice, 
             family = binomial(link = "log"), 
             data = prov1_AQI_4_14)
             )
summary(fit_log0_practice)
fit_log0_practice@beta
```

The random effect for the intercept of practice has zero variance. We omit the fixed effect practice in the model *log1_practice* below.

### Random effect practice, without fixed effect practice

```{r, log1_practice, echo=TRUE}

formula1_practice <- ond ~ pay +(1|practice)

system.time( fit_log1_practice <- glmer(formula1_practice, 
             family = binomial(link = "log"), 
             data = prov1_AQI_4_14)
             )
summary(fit_log1_practice)
fit_log1_practice@beta
```


```{r log0_results, eval=FALSE, echo=FALSE}
#p_values <- summary.glm((fit_log0))$coefficient[,4]
OR <- exp(fit_log0_practice@beta) # exponentiated coefficients 
# CI_fitlog<- confint(fit_log) # 95% CI for the coefficients, takes too long
kable(data.frame(OR, digits = 3, caption = "Results log0"))
```



