---
title: "Table 1 of AQI data"
author: "Michael Andreae"
date: "July, 24, 2015"
output: pdf_document
---
  
# Insurance status predicts antiemetic use 

  We investigate the Hypothesis that insurance status predicets antiemetic use the population in the Public Use File of the Anestehsia Quality Institute with electronic anesthesia records recording antiemetic use.



```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr) # required to set options in Markdown R
library(plyr)
# library(ResourceSelection)
# library(lme4)
# library(nlme)
```



```{r, global_options, echo=FALSE}

# set the directory to the project directory
setwd("C:/Users/Micheal/Dropbox/Professional/AQI/AQI_Analysis")

# set options
opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
```

## Load cleaned dataset *fullAQI_4_14* and *prov1_AQI_4_14*

we load the cleaned larger dataset without and with provider information *fullAQI_4_14.Rdata*, *prov1_AQI_4_14*, which we generated in *import_AQI_14Jul2015.Rmd*   
  
  
```{r, load_clean_dataset, echo=TRUE}
rm(list = ls())
load("Analysis/Data/fullAQI_4_14.Rdata")
load("Analysis/Data/prov1_AQI_4_14.Rdata")
str(fullAQI_4_14)
str(prov1_AQI_4_14)

```

```{r examples_data, echo=FALSE}
data <- read.table(header=TRUE, text='
 subject sex condition before after change
       1   F   placebo   10.1   6.9   -3.2
       2   F   placebo    6.3   4.2   -2.1
       3   M   aspirin   12.4   6.3   -6.1
       4   F   placebo    8.1   6.1   -2.0
       5   M   aspirin   15.2   9.9   -5.3
       6   F   aspirin   10.9   7.0   -3.9
       7   F   aspirin   11.6   8.5   -3.1
       8   M   aspirin    9.5   3.0   -6.5
       9   F   placebo   11.5   9.0   -2.5
      10   M   placebo   11.9  11.0   -0.9
      11   F   aspirin   11.4   8.0   -3.4
      12   M   aspirin   10.0   4.4   -5.6
      13   M   aspirin   12.5   5.4   -7.1
      14   M   placebo   10.6  10.6    0.0
      15   M   aspirin    9.1   4.3   -4.8
      16   F   placebo   12.1  10.2   -1.9
      17   F   placebo   11.0   8.8   -2.2
      18   F   placebo   11.9  10.2   -1.7
      19   M   aspirin    9.1   3.6   -5.5
      20   M   placebo   13.5  12.4   -1.1
      21   M   aspirin   12.0   7.5   -4.5
      22   F   placebo    9.1   7.6   -1.5
      23   M   placebo    9.9   8.0   -1.9
      24   F   placebo    7.6   5.2   -2.4
      25   F   placebo   11.8   9.7   -2.1
      26   F   placebo   11.8  10.7   -1.1
      27   F   aspirin   10.1   7.9   -2.2
      28   M   aspirin   11.6   8.3   -3.3
      29   F   aspirin   11.3   6.8   -4.5
      30   F   placebo   10.3   8.3   -2.0
 ')
```

```{r example_caculations, echo=TRUE}

library(plyr)

# Run the functions length, mean, and sd on the value of "change" for each group, 
# broken down by sex + condition
cdata <- ddply(data, c("sex", "condition"), summarise,
               N    = length(change),
               mean = mean(change),
               sd   = sd(change),
               se   = sd / sqrt(N)
)
kable(cdata)
```

```{r counts_per_strata}
ls()
attach(fullAQI_4_14)
table2 <- ddply(fullAQI_4_14, c("anes_type", "sex", "pay"), summarise,
                N = length(ond)
                #Percent    = length(ond)/sum(ond=="Ondan")
               )
kable(table2)
#LOR <- log(rt/(nt-rt) - log(rc/(nc-rc)

```